MRD_final_microbiome

### 2019-10-04 MRD_final_microbiome .Rmd
updated

# this collapses the two varialbes into a new variable AB in this case. The command for multiple changes is fct_collapse(x, AB = c("A","B"), DE = c("D","E"))
test <- fct_collapse(test, LOW = c("Scandinavia","EasternEurope") , MEDIUM = c("SouthEurope","CentralEurope", "UKIE"), HIGH = c("US") )

@@

@@

Note: Use of transformed/normalised and/or filtered datasets is optional however, it is recommended. IPCO internally check if there are zero abundance features and also check for common features (OTUs/genus/species) between reference taxonomy and queried dataset.
```{r IPCO}

@@

# 2. Normalise/Transform data
# Hellinger transformation
transform_data(pseq, relab)

>>>>

# this collapses the two varialbes into a new variable AB in this case. The command for multiple changes is fct_collapse(x, AB = c("A","B"), DE = c("D","E"))
# test <- fct_collapse(test, LOW = c("Scandinavia","EasternEurope") , MEDIUM = c("SouthEurope","CentralEurope", "UKIE"), HIGH = c("US") )

test <- fct_collapse(test, LOW = c("EasternEurope", "SouthEurope") , MEDIUM = c("CentralEurope"), HIGH = c("US", "UKIE", "Scandinavia") )

@@

test <- fct_collapse(test, LOW = c("EasternEurope", "SouthEurope") , MEDIUM = c("CentralEurope"), HIGH = c("US", "UKIE", "Scandinavia") )

@@

##IPCO
Note: Use of transformed/normalised and/or filtered datasets is optional however, it is recommended. IPCO internally check if there are zero abundance features and also check for common features (OTUs/genus/species) between reference taxonomy and queried dataset.
```{r IPCO}

@@

# 2. Normalise/Transform data
# Hellinger transformation
# transform_data(pseq, relab)

temp <- data("IPCO_Healthy")
